### 2024-02-08 acronyms/acronyms.tex
acronyms
thesis defense presentation

>>>>

\newacronym{eps}{EPSCoR}{Established Program to Stimulate Competitive Research}
\newacronym{nas}{NAS}{National Academies}
\newacronym{brc}{BRC}{Blue Ribbon Commission on America's Nuclear Future}
\newacronym{hlw}{HLW}{High-Level Radioactive Waste}
\newacronym{cbs}{CBS}{Consent-Based Siting}
\newacronym{wpp}{WIPP}{Waste Isolation Pilot Plant}
\newacronym{cfr}{CFR}{Code of Federal Regulations}
